---
title: "ArchR_Analysis_Pt2"
output: html_document
date: "2024-01-17"
---

2nd half of the markdown titled ArchR_Analysis. This basically contains everything that was done AFTER scRNA-scATAC integration. I'll be picking it off with the dataset after removing non-B cells

```{r}
library(ArchR)
library(Seurat)
addArchRThreads(threads = 1)
addArchRGenome("hg38")
options(future.globals.maxSize=100000000000000000000000) 
```
Load existing ArchR project
```{r}
archR <- loadArchRProject(path = "/Users/gagled01/morganLab/Waldenstroms/singlecell/data/ATAC_fragments/ArchR_ReferenceAdd_B-LineageOnly")
```
Rerun LSI, clustering, and batch correction since non B-cells have been excluded
```{r}
archR <- addIterativeLSI(
  ArchRProj = archR,
  useMatrix = "TileMatrix",
  name = "IterativeLSI_BLineage_Recluster",
  iterations = 2,
  clusterParams = list( # based on Seurat's FindClusters()
    resolution = c(0.25),
    sampleCells = 2000,
    n.start = 10
  ),
  varFeatures = 20000,
  dimsToUse = 1:20,
  force = T
)

archR <- addClusters(
  input = archR,
  reducedDims = "IterativeLSI_BLineage_Recluster",
  method = "Seurat",
  name = "BLin_Clusters",
  resolution = 0.9,
  force = T
)

archR <- addUMAP(
    ArchRProj = archR, 
    reducedDims = "IterativeLSI_BLineage_Recluster", 
    name = "BLineage_Recluster_UMAP", 
    nNeighbors = 30, 
    minDist = 0.5, 
    metric = "cosine",
    force = T
)
```
# Dirty way to get celltype relative abundance by patient dataframe for stacked barplots
```{r}
############### NYU SAMPLES
p01.076.ids <- BiocGenerics::which(archR$samplesClean %in% "01-076")
p01.076.celltypes <- archR$predictedGroup_Un[p01.076.ids]
p01.115.ids <- BiocGenerics::which(archR$samplesClean %in% "01-115")
p01.115.celltypes <- archR$predictedGroup_Un[p01.115.ids]
p01.131.ids <- BiocGenerics::which(archR$samplesClean %in% "01-131")
p01.131.celltypes <- archR$predictedGroup_Un[p01.131.ids]
p01.163.ids <- BiocGenerics::which(archR$samplesClean %in% "01-163")
p01.163.celltypes <- archR$predictedGroup_Un[p01.163.ids]
p01.190.ids <- BiocGenerics::which(archR$samplesClean %in% "01-190")
p01.190.celltypes <- archR$predictedGroup_Un[p01.190.ids]
p04.003.ids <- BiocGenerics::which(archR$samplesClean %in% "04-003")
p04.003.celltypes <- archR$predictedGroup_Un[p04.003.ids]
p04.006.ids <- BiocGenerics::which(archR$samplesClean %in% "04-006")
p04.006.celltypes <- archR$predictedGroup_Un[p04.006.ids]

############### GUSTAVE ROUSSY SAMPLES

wm25.ids <- BiocGenerics::which(archR$samplesClean %in% "WM25")
wm25.celltypes <- archR$predictedGroup_Un[wm25.ids]
wm43.ids <- BiocGenerics::which(archR$samplesClean %in% "WM43")
wm43.celltypes <- archR$predictedGroup_Un[wm43.ids]
wm46.ids <- BiocGenerics::which(archR$samplesClean %in% "WM46")
wm46.celltypes <- archR$predictedGroup_Un[wm46.ids]
wm47.ids <- BiocGenerics::which(archR$samplesClean %in% "WM47")
wm47.celltypes <- archR$predictedGroup_Un[wm47.ids]
wm54.ids <- BiocGenerics::which(archR$samplesClean %in% "WM54")
wm54.celltypes <- archR$predictedGroup_Un[wm54.ids]
wm65.ids <- BiocGenerics::which(archR$samplesClean %in% "WM65")
wm65.celltypes <- archR$predictedGroup_Un[wm65.ids]
###############

bcp003.ids <- BiocGenerics::which(archR$samplesClean %in% "BCP003")
bcp003.celltypes <- archR$predictedGroup_Un[bcp003.ids]
bcp004.ids <- BiocGenerics::which(archR$samplesClean %in% "BCP004")
bcp004.celltypes <- archR$predictedGroup_Un[bcp004.ids]
bcp005.ids <- BiocGenerics::which(archR$samplesClean %in% "BCP005")
bcp005.celltypes <- archR$predictedGroup_Un[bcp005.ids]
bcp006.ids <- BiocGenerics::which(archR$samplesClean %in% "BCP006")
bcp006.celltypes <- archR$predictedGroup_Un[bcp006.ids]

###############
stanford1.ids <- BiocGenerics::which(archR$samplesClean %in% "stanford_1")
stanford1.celltypes <- archR$predictedGroup_Un[stanford1.ids]
stanford2.ids <- BiocGenerics::which(archR$samplesClean %in% "stanford_2")
stanford2.celltypes <- archR$predictedGroup_Un[stanford2.ids]
stanford3.ids <- BiocGenerics::which(archR$samplesClean %in% "stanford_3")
stanford3.celltypes <- archR$predictedGroup_Un[stanford3.ids]

# Relative abundance by patient...requires a lot of fennegling bcuz different patients have different cell populations
p01.076_relabun <- data.frame(table(p01.076.celltypes)/sum(table(p01.076.celltypes)) * 100)
p01.076_relabun$Patient <- "01-076"
colnames(p01.076_relabun)[1] <- "Celltype"
missing.celltypes <- setdiff(archR$predictedGroup_Un, p01.076_relabun$Celltype)
missing.df <- data.frame(matrix(NA, nrow = length(missing.celltypes), ncol = 3))
colnames(missing.df) <- c("Celltype", "Freq", "Patient")
missing.df$Celltype <- missing.celltypes
missing.df$Patient <- "01-076"
p01.076.mergedf <- rbind(p01.076_relabun, missing.df)

p01.115_relabun <- data.frame(table(p01.115.celltypes)/sum(table(p01.115.celltypes)) * 100)
p01.115_relabun$Patient <- "01-115"
colnames(p01.115_relabun)[1] <- "Celltype"
# missing.celltypes <- setdiff(archR$predictedGroup_Un, p01.115_relabun$Celltype)
# missing.df <- data.frame(matrix(NA, nrow = length(missing.celltypes), ncol = 3))
# colnames(missing.df) <- c("Celltype", "Freq", "Patient")
# missing.df$Celltype <- missing.celltypes
# missing.df$Patient <- "01-115"
# p01.115.mergedf <- rbind(p01.115_relabun, missing.df)
p01.115.mergedf <- p01.115_relabun # because it has all celltypes!

p01.131_relabun <- data.frame(table(p01.131.celltypes)/sum(table(p01.131.celltypes)) * 100)
p01.131_relabun$Patient <- "01-131"
colnames(p01.131_relabun)[1] <- "Celltype"
missing.celltypes <- setdiff(archR$predictedGroup_Un, p01.131_relabun$Celltype)
missing.df <- data.frame(matrix(NA, nrow = length(missing.celltypes), ncol = 3))
colnames(missing.df) <- c("Celltype", "Freq", "Patient")
missing.df$Celltype <- missing.celltypes
missing.df$Patient <- "01-131"
p01.131.mergedf <- rbind(p01.131_relabun, missing.df)

p01.163_relabun <- data.frame(table(p01.163.celltypes)/sum(table(p01.163.celltypes)) * 100)
p01.163_relabun$Patient <- "01-163"
colnames(p01.163_relabun)[1] <- "Celltype"
missing.celltypes <- setdiff(archR$predictedGroup_Un, p01.163_relabun$Celltype)
missing.df <- data.frame(matrix(NA, nrow = length(missing.celltypes), ncol = 3))
colnames(missing.df) <- c("Celltype", "Freq", "Patient")
missing.df$Celltype <- missing.celltypes
missing.df$Patient <- "01-163"
p01.163.mergedf <- rbind(p01.163_relabun, missing.df)

p01.190_relabun <- data.frame(table(p01.190.celltypes)/sum(table(p01.190.celltypes)) * 100)
p01.190_relabun$Patient <- "01-190"
colnames(p01.190_relabun)[1] <- "Celltype"
missing.celltypes <- setdiff(archR$predictedGroup_Un, p01.190_relabun$Celltype)
missing.df <- data.frame(matrix(NA, nrow = length(missing.celltypes), ncol = 3))
colnames(missing.df) <- c("Celltype", "Freq", "Patient")
missing.df$Celltype <- missing.celltypes
missing.df$Patient <- "01-190"
p01.190.mergedf <- rbind(p01.190_relabun, missing.df)

p04.003_relabun <- data.frame(table(p04.003.celltypes)/sum(table(p04.003.celltypes)) * 100)
p04.003_relabun$Patient <- "04-003"
colnames(p04.003_relabun)[1] <- "Celltype"
# missing.celltypes <- setdiff(archR$predictedGroup_Un, p04.003_relabun$Celltype)
# missing.df <- data.frame(matrix(NA, nrow = length(missing.celltypes), ncol = 3))
# colnames(missing.df) <- c("Celltype", "Freq", "Patient")
# missing.df$Celltype <- missing.celltypes
# missing.df$Patient <- "04-003"
# p04.003.mergedf <- rbind(p04.003_relabun, missing.df)
p04.003.mergedf <- p04.003_relabun # because it has all celltypes!

p04.006_relabun <- data.frame(table(p04.006.celltypes)/sum(table(p04.006.celltypes)) * 100)
p04.006_relabun$Patient <- "04-006"
colnames(p04.006_relabun)[1] <- "Celltype"
missing.celltypes <- setdiff(archR$predictedGroup_Un, p04.006_relabun$Celltype)
missing.df <- data.frame(matrix(NA, nrow = length(missing.celltypes), ncol = 3))
colnames(missing.df) <- c("Celltype", "Freq", "Patient")
missing.df$Celltype <- missing.celltypes
missing.df$Patient <- "04-006"
p04.006.mergedf <- rbind(p04.006_relabun, missing.df)

###################################### GOUSTAV ROUSSY SAMPLES

wm25_relabun <- data.frame(table(wm25.celltypes)/sum(table(wm25.celltypes)) * 100)
wm25_relabun$Patient <- "WM25"
colnames(wm25_relabun)[1] <- "Celltype"
missing.celltypes <- setdiff(archR$predictedGroup_Un, wm25_relabun$Celltype)
missing.df <- data.frame(matrix(NA, nrow = length(missing.celltypes), ncol = 3))
colnames(missing.df) <- c("Celltype", "Freq", "Patient")
missing.df$Celltype <- missing.celltypes
missing.df$Patient <- "WM25"
wm25.mergedf <- rbind(wm25_relabun, missing.df)

wm43_relabun <- data.frame(table(wm43.celltypes)/sum(table(wm43.celltypes)) * 100)
wm43_relabun$Patient <- "WM43"
colnames(wm43_relabun)[1] <- "Celltype"
# missing.celltypes <- setdiff(archR$predictedGroup_Un, wm43_relabun$Celltype)
# missing.df <- data.frame(matrix(NA, nrow = length(missing.celltypes), ncol = 3))
# colnames(missing.df) <- c("Celltype", "Freq", "Patient")
# missing.df$Celltype <- missing.celltypes
# missing.df$Patient <- "Wm43"
# wm43.mergedf <- rbind(wm43_relabun, missing.df)
wm43.mergedf <- wm43_relabun # because it has all celltypes

wm46_relabun <- data.frame(table(wm46.celltypes)/sum(table(wm46.celltypes)) * 100)
wm46_relabun$Patient <- "WM46"
colnames(wm46_relabun)[1] <- "Celltype"
missing.celltypes <- setdiff(archR$predictedGroup_Un, wm46_relabun$Celltype)
missing.df <- data.frame(matrix(NA, nrow = length(missing.celltypes), ncol = 3))
colnames(missing.df) <- c("Celltype", "Freq", "Patient")
missing.df$Celltype <- missing.celltypes
missing.df$Patient <- "WM46"
wm46.mergedf <- rbind(wm46_relabun, missing.df)

wm47_relabun <- data.frame(table(wm47.celltypes)/sum(table(wm47.celltypes)) * 100)
wm47_relabun$Patient <- "WM47"
colnames(wm47_relabun)[1] <- "Celltype"
# missing.celltypes <- setdiff(archR$predictedGroup_Un, wm47_relabun$Celltype)
# missing.df <- data.frame(matrix(NA, nrow = length(missing.celltypes), ncol = 3))
# colnames(missing.df) <- c("Celltype", "Freq", "Patient")
# missing.df$Celltype <- missing.celltypes
# missing.df$Patient <- "WM47"
# wm47.mergedf <- rbind(wm47_relabun, missing.df)
wm47.mergedf <- wm47_relabun # because it has all celltypes

wm54_relabun <- data.frame(table(wm54.celltypes)/sum(table(wm54.celltypes)) * 100)
wm54_relabun$Patient <- "WM54"
colnames(wm54_relabun)[1] <- "Celltype"
# missing.celltypes <- setdiff(archR$predictedGroup_Un, wm54_relabun$Celltype)
# missing.df <- data.frame(matrix(NA, nrow = length(missing.celltypes), ncol = 3))
# colnames(missing.df) <- c("Celltype", "Freq", "Patient")
# missing.df$Celltype <- missing.celltypes
# missing.df$Patient <- "WM54"
# wm54.mergedf <- rbind(wm54_relabun, missing.df)
wm54.mergedf <- wm54_relabun # because it has all celltypes

wm65_relabun <- data.frame(table(wm65.celltypes)/sum(table(wm65.celltypes)) * 100)
wm65_relabun$Patient <- "WM65"
colnames(wm65_relabun)[1] <- "Celltype"
missing.celltypes <- setdiff(archR$predictedGroup_Un, wm65_relabun$Celltype)
missing.df <- data.frame(matrix(NA, nrow = length(missing.celltypes), ncol = 3))
colnames(missing.df) <- c("Celltype", "Freq", "Patient")
missing.df$Celltype <- missing.celltypes
missing.df$Patient <- "WM65"
wm65.mergedf <- rbind(wm65_relabun, missing.df)

###################################### REFERENCE DATA

bcp003_relabun <- data.frame(table(bcp003.celltypes)/sum(table(bcp003.celltypes)) * 100)
bcp003_relabun$Patient <- "BCP003"
colnames(bcp003_relabun)[1] <- "Celltype"
missing.celltypes <- setdiff(archR$predictedGroup_Un, bcp003_relabun$Celltype)
missing.df <- data.frame(matrix(NA, nrow = length(missing.celltypes), ncol = 3))
colnames(missing.df) <- c("Celltype", "Freq", "Patient")
missing.df$Celltype <- missing.celltypes
missing.df$Patient <- "BCP003"
bcp003.mergedf <- rbind(bcp003_relabun, missing.df)

bcp004_relabun <- data.frame(table(bcp004.celltypes)/sum(table(bcp004.celltypes)) * 100)
bcp004_relabun$Patient <- "BCP004"
colnames(bcp004_relabun)[1] <- "Celltype"
missing.celltypes <- setdiff(archR$predictedGroup_Un, bcp004_relabun$Celltype)
missing.df <- data.frame(matrix(NA, nrow = length(missing.celltypes), ncol = 3))
colnames(missing.df) <- c("Celltype", "Freq", "Patient")
missing.df$Celltype <- missing.celltypes
missing.df$Patient <- "BCP004"
bcp004.mergedf <- rbind(bcp004_relabun, missing.df)

bcp005_relabun <- data.frame(table(bcp005.celltypes)/sum(table(bcp005.celltypes)) * 100)
bcp005_relabun$Patient <- "BCP005"
colnames(bcp005_relabun)[1] <- "Celltype"
missing.celltypes <- setdiff(archR$predictedGroup_Un, bcp005_relabun$Celltype)
missing.df <- data.frame(matrix(NA, nrow = length(missing.celltypes), ncol = 3))
colnames(missing.df) <- c("Celltype", "Freq", "Patient")
missing.df$Celltype <- missing.celltypes
missing.df$Patient <- "BCP005"
bcp005.mergedf <- rbind(bcp005_relabun, missing.df)

bcp006_relabun <- data.frame(table(bcp006.celltypes)/sum(table(bcp006.celltypes)) * 100)
bcp006_relabun$Patient <- "BCP006"
colnames(bcp006_relabun)[1] <- "Celltype"
missing.celltypes <- setdiff(archR$predictedGroup_Un, bcp006_relabun$Celltype)
missing.df <- data.frame(matrix(NA, nrow = length(missing.celltypes), ncol = 3))
colnames(missing.df) <- c("Celltype", "Freq", "Patient")
missing.df$Celltype <- missing.celltypes
missing.df$Patient <- "BCP006"
bcp006.mergedf <- rbind(bcp006_relabun, missing.df)

#########################################

stanford1_relabun <- data.frame(table(stanford1.celltypes)/sum(table(stanford1.celltypes)) * 100)
stanford1_relabun$Patient <- "stanford1"
colnames(stanford1_relabun)[1] <- "Celltype"
# missing.celltypes <- setdiff(archR$predictedGroup_Un, stanford1_relabun$Celltype)
# missing.df <- data.frame(matrix(NA, nrow = length(missing.celltypes), ncol = 3))
# colnames(missing.df) <- c("Celltype", "Freq", "Patient")
# missing.df$Celltype <- missing.celltypes
# missing.df$Patient <- "stanford1"
# stanford1.mergedf <- rbind(stanford1_relabun, missing.df)
stanford1.mergedf <- stanford1_relabun # because it has all celltypes

stanford2_relabun <- data.frame(table(stanford2.celltypes)/sum(table(stanford2.celltypes)) * 100)
stanford2_relabun$Patient <- "stanford2"
colnames(stanford2_relabun)[1] <- "Celltype"
# missing.celltypes <- setdiff(archR$predictedGroup_Un, stanford2_relabun$Celltype)
# missing.df <- data.frame(matrix(NA, nrow = length(missing.celltypes), ncol = 3))
# colnames(missing.df) <- c("Celltype", "Freq", "Patient")
# missing.df$Celltype <- missing.celltypes
# missing.df$Patient <- "stanford2"
# stanford2.mergedf <- rbind(stanford2_relabun, missing.df)
stanford2.mergedf <- stanford2_relabun # because it has all celltypes

stanford3_relabun <- data.frame(table(stanford3.celltypes)/sum(table(stanford3.celltypes)) * 100)
stanford3_relabun$Patient <- "stanford3"
colnames(stanford3_relabun)[1] <- "Celltype"
missing.celltypes <- setdiff(archR$predictedGroup_Un, stanford3_relabun$Celltype)
missing.df <- data.frame(matrix(NA, nrow = length(missing.celltypes), ncol = 3))
colnames(missing.df) <- c("Celltype", "Freq", "Patient")
missing.df$Celltype <- missing.celltypes # not missing any types
missing.df$Patient <- "stanford3"
stanford3.mergedf <- rbind(stanford3_relabun)

allpatient_df <- rbind(p01.076.mergedf, p01.115.mergedf, p01.131.mergedf, p01.163.mergedf, p01.190.mergedf, p04.003.mergedf, p04.006.mergedf, 
                       wm25.mergedf, wm43.mergedf, wm46.mergedf, wm47.mergedf, wm54.mergedf, wm65.mergedf,
                       bcp003.mergedf, bcp004.mergedf, bcp005.mergedf, bcp006.mergedf, 
                       stanford1.mergedf, stanford2.mergedf, stanford3.mergedf)
```
# Stacked bar plot of cell type relative abundances
```{r}
# factor so plasma cells come up first
allpatient_df$Celltype <- factor(allpatient_df$Celltype, levels = c("Plasma cells", "Memory B cells", "Naive B cells", "Germinal center B cells", "Proliferative germinal center B cells", "Small pre-B cells", "Large pre-B cells", "Pro-B cells"))

# similar w patients
allpatient_df$Patient <- factor(allpatient_df$Patient, levels = c("01-076", "01-115", "01-131", "01-163", "01-190", "04-003", "04-006",
                                                                  "WM25", "WM43", "WM46", "WM47", "WM54", "WM65",
                                                                  "BCP003", "BCP004", "BCP005", "BCP006",
                                                                  "stanford1", "stanford2", "stanford3"))
allpatient_df$Patient <- droplevels(allpatient_df$Patient)

# Stacked barplot
ggplot(allpatient_df, aes(fill=Celltype, y=Freq, x=Patient)) + 
    geom_bar(position="stack", stat="identity") + 
  xlab(label = "Patient") + ylab("Relative Abundance") + theme_minimal() + 
  theme(axis.text.x = element_text(size = "10", angle = 90, vjust = 0.5, hjust = 0.5))
```
# Temporarily and illegally subset (supposed to use SubsetArchR() function) to get plasma cell %s
```{r}
idxSample <- BiocGenerics::which(archR$predictedGroup_Un %in% "Plasma cells")
cellsSample <- archR$cellNames[idxSample]
illegal.archR.PC <- archR[cellsSample, ]
table(illegal.archR.PC$samplesClean)/table(archR$samplesClean) *100

idxSample <- BiocGenerics::which(archR$predictedGroup_Un %in% "Memory B cells")
cellsSample <- archR$cellNames[idxSample]
illegal.archR.PC <- archR[cellsSample, ]
table(illegal.archR.PC$samplesClean)/table(archR$samplesClean) *100

rm(illegal.archR.PC)
```
# Adding individual patient metadata about clinically known mutations
```{r}
archR$hasPC <- archR$samplesClean
pc.1 <- gsub("01-076", "-", archR$hasPC)
archR$hasPC <- pc.1
pc.2 <- gsub("01-115", "-", archR$hasPC)
archR$hasPC <- pc.2
pc.3 <- gsub("01-131", "+", archR$hasPC)
archR$hasPC <- pc.3
pc.4 <- gsub("01-163", "+", archR$hasPC)
archR$hasPC <- pc.4
pc.5 <- gsub("01-190", "+", archR$hasPC)
archR$hasPC <- pc.5
pc.6 <- gsub("04-003", "+", archR$hasPC)
archR$hasPC <- pc.6
pc.7 <- gsub("04-006", "-", archR$hasPC)
archR$hasPC <- pc.7
pc.8 <- gsub("BCP00.", "NA", archR$hasPC)
archR$hasPC <- pc.8
pc.9 <- gsub("stanford_.", "NA", archR$hasPC)
archR$hasPC <- pc.9
# UPDATE
pc.10 <- gsub("WM25", "+", archR$hasPC)
archR$hasPC <- pc.10
pc.11 <- gsub("WM43", "+", archR$hasPC)
archR$hasPC <- pc.11
pc.12 <- gsub("WM46", "-", archR$hasPC)
archR$hasPC <- pc.12
pc.13 <- gsub("WM47", "-", archR$hasPC)
archR$hasPC <- pc.13
pc.14 <- gsub("WM54", "-", archR$hasPC)
archR$hasPC <- pc.14
pc.15 <- gsub("WM65", "-", archR$hasPC)
archR$hasPC <- pc.15
table(archR$hasPC)

# MYD88 mutations
archR$myd88 <- archR$samplesClean
myd88.1 <- gsub("01-190", "+", archR$myd88)
archR$myd88 <- myd88.1
myd88.2 <- gsub("04-003", "+", archR$myd88)
archR$myd88 <- myd88.2
myd88.3 <- gsub("01-...", "+", archR$myd88)
archR$myd88 <- myd88.3
myd88.4 <- gsub("04-...", "+", archR$myd88)
archR$myd88 <- myd88.4
myd88.5 <- gsub("WM25", "+", archR$myd88)
archR$myd88 <- myd88.5
myd88.6 <- gsub("WM43", "+", archR$myd88)
archR$myd88 <- myd88.6
myd88.7 <- gsub("WM46", "+", archR$myd88)
archR$myd88 <- myd88.7
myd88.8 <- gsub("WM47", "+", archR$myd88)
archR$myd88 <- myd88.8
myd88.9 <- gsub("WM54", "+", archR$myd88)
archR$myd88 <- myd88.9
myd88.10 <- gsub("WM65", "+", archR$myd88)
archR$myd88 <- myd88.10
myd88.11 <- gsub("BCP00.", "NA", archR$myd88)
archR$myd88 <- myd88.11
myd88.12 <- gsub("stanford_.", "NA", archR$myd88)
archR$myd88 <- myd88.12
table(archR$myd88)

# CXCR4 mutations
archR$cxcr4 <- archR$samplesClean
cxcr4.1 <- gsub("01-190", "+", archR$cxcr4)
archR$cxcr4 <- cxcr4.1
cxcr4.2 <- gsub("04-006", "+", archR$cxcr4)
archR$cxcr4 <- cxcr4.2
cxcr4.3 <- gsub("01-...", "-", archR$cxcr4)
archR$cxcr4 <- cxcr4.3
cxcr4.4 <- gsub("04-...", "-", archR$cxcr4)
archR$cxcr4 <- cxcr4.4
cxcr4.5 <- gsub("WM25", "-", archR$cxcr4)
archR$cxcr4 <- cxcr4.5
cxcr4.6 <- gsub("WM43", "+", archR$cxcr4)
archR$cxcr4 <- cxcr4.6
cxcr4.7 <- gsub("WM46", "-", archR$cxcr4)
archR$cxcr4 <- cxcr4.7
cxcr4.8 <- gsub("WM47", "-", archR$cxcr4)
archR$cxcr4 <- cxcr4.8
cxcr4.9 <- gsub("WM54", "-", archR$cxcr4)
archR$cxcr4 <- cxcr4.9
cxcr4.10 <- gsub("WM65", "+", archR$cxcr4)
archR$cxcr4 <- cxcr4.10
cxcr4.11 <- gsub("BCP00.", "NA", archR$cxcr4)
archR$cxcr4 <- cxcr4.11
cxcr4.12 <- gsub("stanford_.", "NA", archR$cxcr4)
archR$cxcr4 <- cxcr4.12
table(archR$cxcr4)

# ARID1A mutations
archR$arid1a <- archR$samplesClean
arid1a.1 <- gsub("01-190", "NA", archR$arid1a)
archR$arid1a <- arid1a.1
arid1a.2 <- gsub("04-003", "NA", archR$arid1a)
archR$arid1a <- arid1a.2
arid1a.3 <- gsub("01-...", "NA", archR$arid1a)
archR$arid1a <- arid1a.3
arid1a.4 <- gsub("04-...", "NA", archR$arid1a)
archR$arid1a <- arid1a.4
arid1a.5 <- gsub("WM25", "-", archR$arid1a)
archR$arid1a <- arid1a.5
arid1a.6 <- gsub("WM43", "-", archR$arid1a)
archR$arid1a <- arid1a.6
arid1a.7 <- gsub("WM46", "-", archR$arid1a)
archR$arid1a <- arid1a.7
arid1a.8 <- gsub("WM47", "+", archR$arid1a)
archR$arid1a <- arid1a.8
arid1a.9 <- gsub("WM54", "-", archR$arid1a)
archR$arid1a <- arid1a.9
arid1a.10 <- gsub("WM65", "-", archR$arid1a)
archR$arid1a <- arid1a.10
arid1a.11 <- gsub("BCP00.", "NA", archR$arid1a)
archR$arid1a <- arid1a.11
arid1a.12 <- gsub("stanford_.", "NA", archR$arid1a)
archR$arid1a <- arid1a.12
table(archR$arid1a)  

# TP53 mutations
archR$tp53 <- archR$samplesClean
tp53.1 <- gsub("01-190", "NA", archR$tp53)
archR$tp53 <- tp53.1
tp53.2 <- gsub("04-003", "NA", archR$tp53)
archR$tp53 <- tp53.2
tp53.3 <- gsub("01-...", "NA", archR$tp53)
archR$tp53 <- tp53.3
tp53.4 <- gsub("04-...", "NA", archR$tp53)
archR$tp53 <- tp53.4
tp53.5 <- gsub("WM25", "-", archR$tp53)
archR$tp53 <- tp53.5
tp53.6 <- gsub("WM43", "-", archR$tp53)
archR$tp53 <- tp53.6
tp53.7 <- gsub("WM46", "-", archR$tp53)
archR$tp53 <- tp53.7
tp53.8 <- gsub("WM47", "-", archR$tp53)
archR$tp53 <- tp53.8
tp53.9 <- gsub("WM54", "-", archR$tp53)
archR$tp53 <- tp53.9
tp53.10 <- gsub("WM65", "+", archR$tp53)
archR$tp53 <- tp53.10
tp53.11 <- gsub("BCP00.", "NA", archR$tp53)
archR$tp53 <- tp53.11
tp53.12 <- gsub("stanford_.", "NA", archR$tp53)
archR$tp53 <- tp53.12
table(archR$tp53)  

# MLL2 mutations
archR$mll2 <- archR$samplesClean
mll2.1 <- gsub("01-190", "NA", archR$mll2)
archR$mll2 <- mll2.1
mll2.2 <- gsub("04-003", "NA", archR$mll2)
archR$mll2 <- mll2.2
mll2.3 <- gsub("01-...", "NA", archR$mll2)
archR$mll2 <- mll2.3
mll2.4 <- gsub("04-...", "NA", archR$mll2)
archR$mll2 <- mll2.4
mll2.5 <- gsub("WM25", "NA", archR$mll2)
archR$mll2 <- mll2.5
mll2.6 <- gsub("WM43", "+", archR$mll2)
archR$mll2 <- mll2.6
mll2.7 <- gsub("WM46", "-", archR$mll2)
archR$mll2 <- mll2.7
mll2.8 <- gsub("WM47", "+", archR$mll2)
archR$mll2 <- mll2.8
mll2.9 <- gsub("WM54", "-", archR$mll2)
archR$mll2 <- mll2.9
mll2.10 <- gsub("WM65", "-", archR$mll2)
archR$mll2 <- mll2.10
mll2.11 <- gsub("BCP00.", "NA", archR$mll2)
archR$mll2 <- mll2.11
mll2.12 <- gsub("stanford_.", "NA", archR$mll2)
archR$mll2 <- mll2.12
table(archR$mll2)  

# hist1h1e mutations
archR$hist1h1e <- archR$samplesClean
hist1h1e.1 <- gsub("01-190", "NA", archR$hist1h1e)
archR$hist1h1e <- hist1h1e.1
hist1h1e.2 <- gsub("04-003", "NA", archR$hist1h1e)
archR$hist1h1e <- hist1h1e.2
hist1h1e.3 <- gsub("01-...", "NA", archR$hist1h1e)
archR$hist1h1e <- hist1h1e.3
hist1h1e.4 <- gsub("04-...", "NA", archR$hist1h1e)
archR$hist1h1e <- hist1h1e.4
hist1h1e.5 <- gsub("WM25", "-", archR$hist1h1e)
archR$hist1h1e <- hist1h1e.5
hist1h1e.6 <- gsub("WM43", "-", archR$hist1h1e)
archR$hist1h1e <- hist1h1e.6
hist1h1e.7 <- gsub("WM46", "+", archR$hist1h1e)
archR$hist1h1e <- hist1h1e.7
hist1h1e.8 <- gsub("WM47", "+", archR$hist1h1e)
archR$hist1h1e <- hist1h1e.8
hist1h1e.9 <- gsub("WM54", "-", archR$hist1h1e)
archR$hist1h1e <- hist1h1e.9
hist1h1e.10 <- gsub("WM65", "+", archR$hist1h1e)
archR$hist1h1e <- hist1h1e.10
hist1h1e.11 <- gsub("BCP00.", "NA", archR$hist1h1e)
archR$hist1h1e <- hist1h1e.11
hist1h1e.12 <- gsub("stanford_.", "NA", archR$hist1h1e)
archR$hist1h1e <- hist1h1e.12
table(archR$hist1h1e)  

p1 <- plotEmbedding(ArchRProj = archR, colorBy = "cellColData", name = "hasPC", embedding = "BLineage_Recluster_UMAP")
p2 <- plotEmbedding(ArchRProj = archR, colorBy = "cellColData", name = "myd88", embedding = "BLineage_Recluster_UMAP")
p3 <- plotEmbedding(ArchRProj = archR, colorBy = "cellColData", name = "cxcr4", embedding = "BLineage_Recluster_UMAP")
p4 <- plotEmbedding(ArchRProj = archR, colorBy = "cellColData", name = "arid1a", embedding = "BLineage_Recluster_UMAP")
p5 <- plotEmbedding(ArchRProj = archR, colorBy = "cellColData", name = "tp53", embedding = "BLineage_Recluster_UMAP")
p6 <- plotEmbedding(ArchRProj = archR, colorBy = "cellColData", name = "mll2", embedding = "BLineage_Recluster_UMAP")
p7 <- plotEmbedding(ArchRProj = archR, colorBy = "cellColData", name = "hist1h1e", embedding = "BLineage_Recluster_UMAP")

plotPDF(p1, p2, p3, p4, p5, p6, p7, name = "WM_ReferenceAddIntegrated_BLineageOnly_MutationStatus_UMAPs.pdf", ArchRProj = archR, addDOC = FALSE, width = 5, height = 5)
```
Pseudo-bulking replicates
```{r}
library("BSgenome.Hsapiens.UCSC.hg38")
archR <- addGroupCoverages(ArchRProj = archR, groupBy = "BLin_NoProgen_Clusters",
                                minRep = 2, maxReplicates = 5, minCells = 40, maxCells = 500, sampleRatio = 0.8)
```
Calling peaks via MACS2
```{r}
# MACS2 must be installed for this method
pathToMacs2 <- findMacs2()

archR <- addReproduciblePeakSet(
    ArchRProj = archR, 
    groupBy = "BLin_NoProgen_Clusters",
    pathToMacs2 = pathToMacs2
)

archR <- addPeakMatrix(archR)
```
Adding chromVAR deviations based on CIRSBP motifs
```{r}
archR <- addMotifAnnotations(ArchRProj = archR, motifSet = "cisbp", name = "Motif")

archR <- addBgdPeaks(archR)

archR <- addDeviationsMatrix(
  ArchRProj = archR, 
  peakAnnotation = "Motif",
  force = TRUE
)
```
Save it out
```{r}
saveArchRProject(ArchRProj = archR, outputDirectory = "WM_2024_PeaksChromVar", load = FALSE)
```

