---
title: "scRNA_Integration"
output: html_document
date: "2023-08-03"
---

Doing an integrated analysis with SCTransform. As per - https://satijalab.org/seurat/articles/integration_introduction.html
Involves running SCTransform on filtered ctrl data, then on WM data. Then selecting integration anchors, finding integration anchors, and integrating.
Had some serious difficulty getting FindIntegrationAnchors to run. Ultimately had to run "rpca" reduction AND specify the dims to use to match those used in SCTransform

Load libraries
```{r}
library(Seurat)
library(ggplot2)
library(dplyr)
options(future.globals.maxSize=10000000000000000)
```
Load data
```{r}
wm.rna <- readRDS("/Users/gagled01/morganLab/Waldenstroms/singlecell/objects/scRNA_WM_MergedQCFiltered.rds")
ctrl.rna <- readRDS("/Users/gagled01/morganLab/Waldenstroms/singlecell/objects/scRNA_Ctrl_MergedQCFiltered.rds")
```
SCTransform on both WM and ctrl
```{r}
ctrl.rna <- SCTransform(ctrl.rna, assay = "RNA", new.assay.name = "SCT", vst.flavor = "v2", ncells = 5000, vars.to.regress = "batch", method = "glmGamPoi") %>%
  RunPCA(npcs = 20) %>%
  RunUMAP(reduction = "pca", dims = 1:20) %>%
  FindNeighbors(reduction = "pca", dims = 1:20) %>%
  FindClusters(resolution = 0.7)

wm.rna <- SCTransform(wm.rna, assay = "RNA", new.assay.name = "SCT", vst.flavor = "v2", ncells = 5000, vars.to.regress = "batch", method = "glmGamPoi", verbose = F) %>%
  RunPCA(npcs = 20)
```
Integration set up
```{r}
ifnb.list <- list(ctrl = ctrl.rna, stim = wm.rna)
features <- SelectIntegrationFeatures(object.list = ifnb.list)
ifnb.list <- PrepSCTIntegration(object.list = ifnb.list, anchor.features = features)
rm(wm.rna, ctrl.rna)
```
Perform integration
```{r}
anchors <- FindIntegrationAnchors(object.list = ifnb.list, normalization.method = "SCT", reduction = "rpca",
    anchor.features = features, dims = 1:20)
integrated <- IntegrateData(anchorset = anchors, normalization.method = "SCT", dims = 1:20)
```
Integrated Analysis
```{r}
integrated <- RunPCA(integrated, dims = 1:20)
integrated <- RunUMAP(integrated, reduction = "pca", dims = 1:20)
integrated <- FindNeighbors(integrated, reduction = "pca", dims = 1:20)
integrated <- FindClusters(integrated, resolution = 0.7)
DimPlot(integrated, reduction = "umap")
```
Bonus adding forgetten metadata
```{r}
integrated@meta.data$case.control <- integrated@meta.data$source
integrated@meta.data$case.control[integrated@meta.data$source == "NYU"] <- "WM"
integrated@meta.data$case.control[integrated@meta.data$source == "Stanford"] <- "HD"
table(integrated@meta.data$case.control)
```
Save out
```{r}
saveRDS(integrated, "/Users/gagled01/morganLab/Waldenstroms/singlecell/objects/scRNA_SCTransformed_Integrated.rds")
```